---
title: "drawer R Markdown demos"
author: "Le Zhang"
date: "2/28/2021"
output: html_document
---

```{css, echo=FALSE, eval=TRUE}
body {
    max-width: 2000px !important;
}
.main-container {
  max-width: 90vw !important;
  margin-left: auto;
  margin-right: auto;
}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simple usage

{[drawer](https://github.com/lz100/drawer)} is compatible with R markdown. If you 
only want a portable image editting tool, you can do it as simple as:

```{r}
library(drawer)
library(ggplot2) # we will make some plots later
canvas("simple_canvas", rmarkdown = TRUE)
```

<p class="text-danger">When you use source code to reproduce this R markdown, open it in **browser** instead of the built-in viewer in **Rstudio**. canvas will be as expected in buil-in the viewer.</p>

## Capture buttons

To capture pictures or plots in the docuemnt to canvas to do further editing:

### `toCanvasBtn`
**1. Create some elements in R markdown with some HTML identifier, like HTML `id`, **
**or other advanced CSS selector (read help file `?canvas`).**

Lets create some plots, remeber to create some identifiers for them. In R markdown,
the easiest way is to create `id` by adding `out.extra='id="xx"'` tag in your 
R chunk setting: `{r out.extra='id="plot1"'}`

````md
```{r echo=FALSE, out.extra='id="plot1"'}`r ''`
ggplot(mpg, aes(cty, hwy)) +
  geom_count(col="tomato3", show.legend=F)
```
````


```{r echo=FALSE, out.extra='id="plot1"'}
ggplot(mpg, aes(cty, hwy)) +
  geom_count(col="tomato3", show.legend=F)
```


**2. Create the capture buttons, or the capture text buttons.**

```{r}
toCanvasBtn(
  dom = "plot1",
  canvasID = "simple_canvas"
)
```

We are telling the button to capture screenshots of "plot1" and send it to canvas.
Now, **click on the button and then scroll back to the canvas**. You should see it 
has been added to the "Images/Plots" left sidebar. Then, you can simply drag the 
image from the list to canvas and start your editing.

This button also allows you to download the screenshot as a *png* or *jpg*. 

**3. Capture more than just an image**

You can capture any HTML element/chunks to the canvas, for example we have some text 
in Rmakrdown (for better capture, we also change the display CSS style a little):

<div id = "some_text"  style="display:inline-block">
#### This is a title in Rmarkdown
some text follows....

- a list
- b
- c
</div>

```{html eval=FALSE}
<div id="some_text" style="display:inline-block">
#### This is a title in Rmarkdown
some text follows....

- a list
- b
- c
</div>
```

```{r}
toCanvasBtn(
  dom = "some_text",
  canvasID = "simple_canvas"
)
```


### `toCanvasTextBtn`

The `toCanvasTextBtn` allows users to capture any elements in current document. 
So, instead of the author of the Rmarkdown who specifies which element to capture, 
this time, users/readers can decide what to capture by fill in the text-input. 

```{r out.extra='id="plot2"'}
ggplot(mpg, aes(cty, hwy)) +
    geom_point()
```

Another plot with `id='plot2'` has created, now first use the text button group below 
to capture it.

```{r}
toCanvasTextBtn(
  canvasID = "simple_canvas",
  text_value = "#plot2",
  style = "width: 50%"
)
```

Then change it to "#plot1" see if you could capture the previous plot by this button.

The thing to notice here is it uses CSS selector, so for `id`, you need to append 
`#` in front `#element_id`. Of course, you can advanced selectors to select elements 
that have no `id`. Learn them by Google "CSS selector".












